---
title: "MATH423_A2_Q2"
output: word_document
---

Reading in the data and setting up the variables 
```{r}
file1 <- "http://www.math.mcgill.ca/yyang/regression/data/salary.csv"
salary <- read.csv(file1, header = TRUE)
x1 <- salary$SPENDING/1000
y1 <- salary$SALARY
fit.Salary <- lm(y1 ~ x1)
summary(fit.Salary)
```

Question 2.1 
```{r}
#Plotting the residuals 
plot(x1,residuals(fit.Salary))
abline(h=0,col='red',lty=2)
```

Looking at this residual plot we are able to see that the data points are not closely clustered around 0, which is a requirement for the residual plot. However, the residuals do not demonstrate any obvious patter. There are a few outliers but they do not greatly hinder the quality of the residual plot. 

Question 2.2
```{r}
qqnorm(residuals(fit.Salary))
```

From this Q-Q plot we are able to see that the residuals do fit a normal distribution because they form a straight line, which is a requirement for a Gaussian Q-Q plot. 

Question 2.3
```{r}
fit.Salary <- lm(y1 ~ x1)
residuals.Salary <- residuals(fit.Salary)
fitted.Salary <- fitted(fit.Salary)
sum(residuals.Salary) #sum of residuals 

sum(x1*residuals.Salary) #sum of x times residuals 

sum(fitted.Salary*residuals.Salary) #sum of fitted values times residuals 

#All of these are small, so we're good. 
```

Question 2.4
```{r}
summary(fit.Salary)
```

From the above summary of fit.Salary we are able to see that the estimators for beta hat not and beta hat one are as follows: 

beta hat not: 12129.4
beta hat one: 3307.6 

Analysis: 
Both p values beta hat not and beta hat one are very small, so we can say that the estimates for beta hat not and beta hat one are significant and strong/good estimators. 

Question 2.5 

Let us say that our null hypothesis H_0: Beta_1 = 0 and the alternative H_1: Beta_1 != 0 (where != means does not equal)
Looking at the summary from Question 2.4 we can see that the p-value of 2.71e-14 is less than the alpha level of 0.05, which indicates that we reject the null hypothesis. Therefore, there is a statistically significant relationship between SPENDING and SALARY at an alpha level of 0.05. 

Question 2.6 
```{r}
error <- qt(0.90,df=49)*311.7 
left <- 3307.6-error #2902.680
right <- 3307.6+error #3712.519 
```

From the above calculations we have that a 90% confidence interval for Beta_1 is [2902.680 , 3712.519]. Therefore we can say that we are 90% confident that the true value for Beta_1 falls within this interval.

Question 2.7 

From this model we have that the fitted model is as follows: 

SALARY = 12129.4 + 3307.6 * SPENDING 

Therefore, the salary of a teacher whose spending per student is 4800$ is: 

SALARY = 12129.4 + 3307.6 * 4800 = 15,888,609 USD 
